\documentclass[oneside,twocolumn]{article}
\usepackage{mathtools}

%% ADD PACKAGES %%

\title{Attributes tagging for Open wells.}
\author{Kipa Tachak}
\date{Thursday  6 June 2019}

\setcounter{secnumdepth}{1}
\newcommand{\tsub}[2]{\text{#1}_{\text{#2}}}
\newcommand{\tsubb}[2]{#1_{\text{#2}}}
\newcommand{\dsub}[2]{\dfrac{\text{#1}}{\text{#2}}}
\newenvironment{ttable}
{
\begin{center}
\begin{tabular}{c|c}
\hline
}
{
\\ \hline
\end{tabular}
\end{center}
}

\begin{document}
\maketitle

%% BODY %%
\section{About the document}
This file documents the process of asset tagging for the asset
'Bore wells' in the category 'Water and
Sanitation'.
\section{Attributes and questions}
There are three sections 'Observation', 'General', and 'Specific'
, each containing their own list of variables and sub-parameters.
For each sub-parameter, there is associated a question for
gathering data related to that sub-parameter.

Since, the structure and to some extend the content of questions
in Observation and General are similar to other assets, we will
analyze from these sections only the variables which differ
significantly from that in other assets. As always, in-depth analysis of section 'Specific' will be given.

The list of variables and questions that will be analyzed is given below:
\begin{itemize}
	\item Observation
	\item General
	\item Specific:
	\begin{enumerate}
		\item Structure Type: What type of open well it is by your observation?
		\item Ownership: Who built the open well?
		\item Security: What is the material that is used to case the Open well?
		\item Connection Type: The Open well is connected to which of the following assets?
		\item Tools: How people fetch water from the open well?
		\item Caution: What is the depth of the open well that you can observe?
		\item Cross connections: What are the assets that you can observe near the open well?
		\item Usage: Are people using the open well on a regular basis?
		\item Quality: Would you drink the water from this open well?
		\item Charges: Are there any charges which come when getting water from this open well?
		\item Maintenance: What is the frequency of technical maintenance or safety audit? 
	\end{enumerate}
\end{itemize}

\section{Overall scoring}
The overall scoring of the asset is given as:
\begin{align*}
	\tsub{Score}{asset} &= \tsubb{W}{observation} \times \tsub{Score}{observation} \\
	&+\tsubb{W}{general} \times \tsub{Score}{general} \\
	&+ \tsub{W}{specific} \times \tsub{Score}{specific}
\end{align*}
\section{Attribute scoring and the process}
\subsection{Specific}
\subsubsection{Structure Type}
\paragraph{What type of open well it is by your observation?}
The options given are,
\begin{ttable}
	Open well type & Rank \\ \hline
	Deep & 1 \\
	Shallow & 2 \\ \hline
	Max. Rank & 2
\end{ttable}
The score is calculated as,
\[
	\tsub{Score}{structure} = \dsub{Rank of selected}{Max. Rank}.
\]

\subsubsection{Ownership}
\paragraph{Who built the open well?}
This is a multi-choice, multi-select question. The options given are,
\begin{ttable}
	Built by & Rank \\ \hline
	Naturally found & 1 \\
	Missionaries & 2 \\
	NGOs & 3 \\
	Communities & 4 \\
	Government & 5 \\ \hline
	Sum of ranks & 15
\end{ttable}
The score is given as,
\[
	\tsub{Score}{ownership} = \dsub{Sum of selected}{Sum of ranks}
\]
\subsubsection{Security}
\paragraph{What is the material that is used to case the open well?}
The options given are,
\begin{ttable}
	Material & Rank \\ \hline
	None & 0 \\
	Others & 1 \\
	Steel sheets & 2 \\
	Rock like structures & 3 \\
	Cement & 4 \\
	PVC & 5 \\
	Iron grills & 6 \\ \hline
	Max. rank & 6 
\end{ttable}
The score is given as,
\[
	\tsub{Score}{security} = \dsub{Rank of selected}{Max. Rank}
\]

\subsubsection{Connection Type}
\paragraph{The open well is connected to which of the following assets?}
This is a multi-choice multi-select question. The options are given as,
\begin{ttable}
	Connected Asset & Rank \\ \hline
	None & 0 \\
	Others & 1 \\
	Hand pump & 2 \\
	Storage tank & 3 \\
	Over ground tank & 4 \\
	Under ground tank & 5 \\
	Over head tank & 6 \\ \hline
	Max. rank & 6
\end{ttable}
The score is given as,
\[
	\tsub{Score}{connect. type} = \dsub{Rank of selected}{Max. Rank}
\]

\subsubsection{Tools}
\paragraph{How people fetch water from the open well?}
This is a multi-choice, multi-select question. The options are given as,
\begin{ttable}
	Fetching method & Rank \\ \hline
	None & 0 \\
	Others & 1 \\
	Bamboo buckets & 2 \\
	Simple bucket and rope & 3 \\
	Pulley & 4 \\
	Electrical Motor & 5 \\
	Solar Run motor & 6 \\ \hline
	Sum of ranks. & 21
\end{ttable}

The score is given as,
\[
	\tsub{Score}{tools} = \dsub{Sum of selected}{Sum of ranks}
\]

\subsubsection{Caution}
\paragraph{What is the depth of the open well that you can observe?}
The options given are,
\begin{ttable}
	Depth & Rank \\ \hline
	30-50m & 4 \\
	51-70m & 3 \\
	91-120m & 2 \\
	121-150m & 1 \\
	Above 150m & 0 \\ \hline
	Max. rank & 4
\end{ttable}
Since, the more deep a open well is, the more dangerous and requirement for caution. Therefore, more dangerous open wells will have lower score. The scoring is given as,
\[
	\tsub{Score}{caution} = \dsub{Rank of selected}{Max. rank}.
\]
\subsubsection{Cross connections}
\paragraph{What are the assets that you can observe near the open well?}
The options given are,
\begin{ttable}
	Assets & Rank \\ \hline
	Waste Disposal Ground & 0 \\
	Fertilizer Storage & 1 \\
	Septic Tank & 2 \\
	Burial Ground & 3 \\
	Livestock yard & 4 \\
	None & 5 \\ \hline
	Sum of ranks & 15
\end{ttable}

The score is calculated as,
\[
	\tsub{Score}{cross conn.} = \dsub{Sum of selected options}{Sum of ranks}
\]

\subsubsection{Usage}
\paragraph{Are people using this open well on a regular basis?}
The usage of the open well is captured by the following equation.
\begin{align*}
	\tsub{Regular}{usage} &= 0, \text{If no.} \\
	&= 1, \text{If yes.}
\end{align*}

Now the option for purpose of use are given as,
\begin{ttable}
	Purpose & Rank \\ \hline
	Other & 1 \\
	Drinking & 2 \\
	Farming & 3 \\
	Livestock & 4 \\ \hline
	Sum of ranks & 10
\end{ttable}
Then, the score for usage is given as,
\[
	\tsub{Score}{usage} = \tsub{Regular}{usage} \times \dsub{Sum of selected}{Sum of ranks}
\]

\subsubsection{Condition}
\paragraph{Were people drinking water from this open well while you visited this spot?}
\begin{align*}
	\tsub{Score}{condition} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}

\subsubsection{Quality}
\paragraph{Would you drink the water from this open well?}
\begin{align*}
	\tsub{Score}{quality} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}

\subsubsection{Charges}
\paragraph{Are there any charges which come when getting water from this open well?}
The presence/absence of charges is given as,
\begin{align*}
	\text{Pr}{charges} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}
Then, the score for water charges is given as,
\begin{align*}
	\tsub{Score}{charges} &= 0, \tsubb{Ch}{water} \ge \text{Threshold} \\
	&= 1 - \Big( \dfrac{\tsubb{Ch}{water}}{\text{Threshold}} \Big), \text{Otherwise}.
\end{align*}
where,
\[
	\tsubb{Ch}{water} = \text{Charges on water in rupees}.
\]
\subsubsection{Maintenance}
\paragraph{What is the frequency of technical maintenance or safety audit?}
The options for technical maintenance are,
\begin{ttable}
	Maintenance Frequency & Rank \\ \hline
	Never & 0 \\
	Others & 1 \\
	Irregular & 2 \\
	Yearly & 3 \\
	Monthly & 4 \\ \hline
	Max. rank & 4 
\end{ttable}
The score for technical maintenance is,
\[
	\tsub{Score}{technical maint.} = \dsub{Rank of selected}{Max. Rank}.
\]

The options for safety audit are,
\begin{ttable}
	Audit Frequency & Rank \\ \hline
	Never & 0 \\
	Others & 1 \\
	Irregular & 2 \\
	Yearly & 3 \\
	Monthly & 4 \\ \hline
	Max. rank & 4 
\end{ttable}
The score for safety audit is given as,
\[
	\tsub{Score}{safety audit} = \dsub{Rank of selected}{Max. Rank}.
\]

The overall score for maintenance is,
\begin{align*}
	\tsub{Score}{maintenance} &= \tsubb{W}{technical maint.} \times \tsub{Score}{technical maint.} \\
	&+ \tsubb{W}{safety audit} \times \tsub{Score}{safety audit}.
\end{align*}

\end{document}

