\documentclass[oneside,twocolumn]{article}
\usepackage{mathtools}

%% ADD PACKAGES %%

\title{Attributes tagging for Public Taps/Public Stand Pod.}
\author{Kipa Tachak}
\date{Thursday  6 June 2019}

\newcommand{\tsub}[2]{\text{#1}_{\text{#2}}}
\newcommand{\tsubb}[2]{#1_{\text{#2}}}
\newcommand{\dsub}[2]{\dfrac{\text{#1}}{\text{#2}}}
\newenvironment{ttable}
{
\begin{center}
\begin{tabular}{c|c}
\hline
}
{
\\ \hline
\end{tabular}
\end{center}
}

\begin{document}
\maketitle

%% BODY %%
\section{About the document}
This file documents the process of asset tagging for the asset
'Public Taps/Public Stand Pod' in the category 'Water and
Sanitation'.
\section{Attributes and questions}
There are three sections 'Observation', 'General', and 'Specific'
, each containing their own list of variables and sub-parameters.
For each sub-parameter, there is associated a question for
gathering data related to that sub-parameter.

Since, the structure and to some extend the content of questions
in Observation and General are similar to other assets, we will
analyze from these sections only the variables which differ
significantly from that in other assets. As always, in-depth analysis of section 'Specific' will be given.

The list of variables and questions that will be analyzed is given below:
\begin{itemize}
	\item General:
		\begin{itemize}
			\item Sanitation:
				\begin{enumerate}
					\item Waste Management: Where does the waste water generated from the asset goes to?
				\end{enumerate}
		\end{itemize}
	\item Specific:
		\begin{itemize}
			\item Availability:
				\begin{enumerate}
					\item Asset condition: Is that Tap in working condition?
					\item Asset condition: Is check valve working in the tap?
					\item Rate of Discharge: How far is the tap from the water tank/source?
					\item Capacity: What is the diameter of the pipe?
					\item Discharge Rate: How many taps are connected to one stand-pod?
					\item Discharge Rate: What is the length of the service tap?
					\item Infrastructure: What is the basement/foundation made of?
					\item Durability: Is there any rust on the tap?
					\item Condition: Were people drinking water while you visited this spot?
					\item Quality: Would you drink the water?
					\item Charges: Are there any charges which come when getting water from this tap?
					\item Maintenance: What is the frequency of technical maintenance or safety audit? 
				\end{enumerate}
		\end{itemize}
\end{itemize}

\section{Overall scoring}
The overall scoring of the asset is given as:
\begin{align*}
	\tsub{Score}{asset} &= \tsubb{W}{observation} \times \tsub{Score}{observation} \\
	&+\tsubb{W}{general} \times \tsub{Score}{general} \\
	&+ \tsub{W}{specific} \times \tsub{Score}{specific}
\end{align*}
\section{Attribute scoring and the process}
\subsection{General}
In General section we will consider only 'Waste Management'. The scoring for waste management is given as follows.
\paragraph{Waste Management: Where does the waster water generated from the asset goes to?}
The available options for discarding waste water generated from the asset is given as,
\begin{ttable}
	Options & Rank \\ \hline
	None & 0 \\
	Others & 1 \\
	Discarded in open field & 2 \\
	Mixes with near by waste bodies & 3 \\
	Discarded in govt. designated structures & 4 \\ \hline
	Sum of ranks & 10  
\end{ttable}

The scoring is done as,
\[
	\tsub{Score}{waste management} = \dsub{Sum of selected options}{Sum of ranks}.
\]

\subsection{Availability}
\subsubsection{Asset condition}
The overall scoring of the asset condition is given as,
\begin{align*}
	\tsub{Score}{asset condition} &= \tsubb{W}{tap condition} \times \tsub{Score}{tap condition} \\
	&+ \tsubb{W}{valve condition} \times \tsub{Score}{valve condition}
\end{align*}
The questions associated with this sub-parameter are discussed below.
\paragraph{Is the tap in working condition?} 
This is a binary yes/no question. The scoring is done as,
\begin{align*}
	\tsub{Score}{tap condition} &= 0, \text{If tap not in working condition}. \\
	&= 1, \text{otherwise}.
\end{align*}

\paragraph{Is check valve working in the tap?}
This is also a binary yes/no question and the scoring is done as,
\begin{align*}
	\tsub{Score}{valve condition} &= 0, \text{If no} \\
	&= 1, \text{If yes}.
\end{align*}

\subsubsection{Rate of discharge}
\paragraph{How far is the tap from the water tank/Source?}
The options available are,
\begin{ttable}
	Options & Rank \\ \hline
	Below 200m & 3 \\
	Between 200-500m & 2 \\
	Above 500m & 1 \\ \hline
	Max. rank & 3 
\end{ttable}
The score is given as,
\[
	\tsub{Score}{discharge rate} = \dsub{Rank of selected}{Max. rank}
\]

\subsubsection{Capacity}
\paragraph{What is the diameter of the pipe?}
This is a multiple-choice single-select question. The options are given as follows,
\begin{ttable}
	Diameter options & Rank \\ \hline
	Others & 1 \\
	12 mm & 2 \\
	24 mm & 3 \\
	36 mm & 4 \\
	48 mm & 5 \\ \hline
	Max. Rank & 5 
\end{ttable}
The score is calculated as,
\[
	\tsub{Score}{capacity} = \dsub{Rank of selected}{Max. rank}.
\]

\subsubsection{Discharge rate}
The score for discharge rate is calculated as,
\begin{align*}
	\tsub{Score}{discharge rate} &= \tsubb{W}{no. of taps} \times \tsub{Score}{no. of taps} \\
	&+ \tsubb{W}{length} \times \tsub{Score}{length}.
\end{align*}
\paragraph{How many taps are connected to one stand pod?}
The options given are,
\begin{ttable}
	Options (no. of taps) & Rank \\ \hline
	1 & 1 \\
	2 & 2 \\
	3 & 3 \\
	4 & 4 \\
	Above 5 & 5 \\ \hline
	Max. rank & 5 
\end{ttable}
The score is calculated as,
\[
	\tsub{Score}{no. of taps} = \dsub{Rank of selected}{Max. rank}
\]
\paragraph{What is the length of the service tap?}
The input to this question is numeric. The score is calculated as,
\begin{align*}
	\tsub{Score}{length} &= 1, \tsubb{L}{tap} \ge \text{Threshold} \\
	&= \sqrt{\dfrac{\tsubb{L}{tap}}{\text{Threshold}}}, \text{Otherwise}.
\end{align*}

\subsubsection{Infrastructure}
\paragraph{What is the basement/foundation made of?}
The available options are,
\begin{ttable}
	Material & Rank \\ \hline
	Others & 1 \\
	Rock like structure & 2 \\
	Cement & 3 \\
	Bricks & 4 \\ \hline
	Sum of ranks & 10 
\end{ttable}
This is a multiple-choice multiple-select question. The scoring is done as,
\[
	\tsub{Score}{infrastructure} = \dsub{Sum of selected options}{Sum of ranks.}
\]

\subsubsection{Durability}
\paragraph{Is there any rust on the tap?}
The score is given as,
\begin{align*}
	\tsub{Score}{durability} &= 0, \text{If yes} \\
	&= 1, \text{if no}.
\end{align*}
\subsubsection{Condition}
\paragraph{Were people drinking water while you visited this spot?}
\begin{align*}
	\tsub{Score}{condition} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}

\subsubsection{Quality}
\paragraph{Would you drink the water?}
\begin{align*}
	\tsub{Score}{quality} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}

\subsubsection{Charges}
The presence/absence of charges is given as,
\begin{align*}
	\text{Pr}{charges} &= 0, \text{If no} \\
	&= 1, \text{if yes}.
\end{align*}
Then, the score for water charges is given as,
\begin{align*}
	\tsub{Score}{charges} &= 0, \tsubb{Ch}{water} \ge \text{Threshold} \\
	&= 1 - \Big( \dfrac{\tsubb{Ch}{water}}{\text{Threshold}} \Big), \text{Otherwise}.
\end{align*}
where,
\[
	\tsubb{Ch}{water} = \text{Charges on water in rupees}.
\]
\subsubsection{Maintenance}
\paragraph{What is the frequency of technical maintenance or safety audit?}
The options for technical maintenance are,
\begin{ttable}
	Maintenance Frequency & Rank \\ \hline
	Never & 0 \\
	Others & 1 \\
	Irregular & 2 \\
	Yearly & 3 \\
	Monthly & 4 \\ \hline
	Max. rank & 4 
\end{ttable}
The score for technical maintenance is,
\[
	\tsub{Score}{technical maint.} = \dsub{Rank of selected}{Max. Rank}.
\]

The options for safety audit are,
\begin{ttable}
	Audit Frequency & Rank \\ \hline
	Never & 0 \\
	Others & 1 \\
	Irregular & 2 \\
	Yearly & 3 \\
	Monthly & 4 \\ \hline
	Max. rank & 4 
\end{ttable}
The score for safety audit is given as,
\[
	\tsub{Score}{safety audit} = \dsub{Rank of selected}{Max. Rank}.
\]

The overall score for maintenance is,
\begin{align*}
	\tsub{Score}{maintenance} &= \tsubb{W}{technical maint.} \times \tsub{Score}{technical maint.} \\
	&+ \tsubb{W}{safety audit} \times \tsub{Score}{safety audit}.
\end{align*}

\end{document}

