\documentclass[oneside,twocolumn]{article}
\usepackage{mathtools}

%% ADD PACKAGES %%

\title{Attributes tagging for Community Hall}
\author{Kipa Tachak}
\date{Saturday  8 June 2019}

\setcounter{secnumdepth}{3}
\newcommand{\tsub}[2]{\text{#1}_{\text{#2}}}
\newcommand{\tsubb}[2]{#1_{\text{#2}}}
\newcommand{\dsub}[2]{\dfrac{\text{#1}}{\text{#2}}}
\newcommand{\multsel}[1]
{
	\[
		\tsub{Score}{#1} = \dsub{Sum of selected}{Sum of ranks}
	\]
}
\newcommand{\singsel}[1]
{
	\[
		\tsub{Score}{#1} = \dsub{Rank of selected}{Max. rank}.
	\]
}
\newenvironment{ttable}
{
\begin{center}
\begin{tabular}{c|c}
\hline
}
{
\\ \hline
\end{tabular}
\end{center}
}

\begin{document}
\maketitle

%% BODY %%
\section{About the document}
This file documents the process of asset tagging for the asset 'Community Hall' in the vertical 'Panchayati Raj'.

\section{Attributes and questions}
The list of sections, variables, and questions are:
\begin{itemize}
	\item Observation
	\item General
	\item Asset Specific
		\begin{itemize}
			\item Infrastructure
				\begin{enumerate}
					\item Capacity: What is the area of that community hall (in square meters)?
					\item Maintenance: Is staff appointed for its maintenance?
				\end{enumerate}
			\item Availability
				\begin{enumerate}
					\item Services: Which of the following is available there?
				\end{enumerate}
			\item Usability
				\begin{enumerate}
					\item Purpose: What purpose is the community hall used for?
				\end{enumerate}
		\end{itemize}
\end{itemize}

\section{Overall scoring}
The overall scoring of the asset is given as,
\begin{align*}
	\tsub{Score}{asset} &= \tsubb{W}{observation} \times \tsub{Score}{observation} \\
	&+ \tsubb{W}{general} \times \tsub{Score}{general} \\
	&+ \tsubb{W}{specific} \times \tsub{Score}{specific}.
\end{align*}

The score of a section or a variable is given as,
\[
	\tsub{Score}{var} = \sum_{l \in P} \tsubb{W}{l} \times \tsub{Score}{l}.
\]
where,
\[
	P = \text{Set of sub-parameter labels.}
\]	

\section{Attribute scoring and the process}
\subsection{Asset Specific}
\subsubsection{Infrastructure}
\paragraph{Capacity: What is the area of the community hall (in square meters)?}
The score is given as,
\begin{align*}
	\tsub{Score}{capacity} &= 1, \tsubb{A}{comm. hall} \ge \text{Threshold} \\
	&= \Big( \dfrac{\tsubb{A}{comm. hall}}{\text{Threshold}} \Big)^{2}, \text{Otherwise}.
\end{align*}
Where,
\[
	\tsubb{A}{comm. hall} = \text{Area of community hall in square meters.}
\]	
\paragraph{Maintenance: Is staff appointed for its maintenance?}
The score is given as,
\begin{align*}
	\tsub{Score}{maintenance} &= 0, \text{if no} \\
	&= 1, \text{if yes}.
\end{align*}
\subsubsection{Availability}
\paragraph{Services: Which of the following is available there?}
The options given are,
\begin{ttable}
	Options & Rank \\ \hline
	Roofed hall & 1 \\
	Rest room & 2 \\
	Proper electricity & 3 \\ \hline
	Max. rank & 3
\end{ttable}
The score is given as,
\singsel{availability}

\subsubsection{Usability}
\paragraph{Purpose: What purpose is the community hall used for?}
The options given are,
\begin{ttable}
	Purpose & Rank \\ \hline
	Others & 1 \\
	Personal use of the people & 2 \\
	Recreational activities for the community & 3 \\
	Panchayat and community meetings & 4 \\ \hline
	Sum of ranks & 10
\end{ttable}
The score is calculated,
\multsel{usability}

\end{document}

