\documentclass[oneside,twocolumn]{article}
\usepackage{mathtools}

%% ADD PACKAGES %%

\title{Attributes tagging for Information Center}
\author{Kipa Tachak}
\date{Saturday  8 June 2019}

\setcounter{secnumdepth}{3}
\newcommand{\tsub}[2]{\text{#1}_{\text{#2}}}
\newcommand{\tsubb}[2]{#1_{\text{#2}}}
\newcommand{\dsub}[2]{\dfrac{\text{#1}}{\text{#2}}}
\newcommand{\multsel}[1]
{
	\[
		\tsub{Score}{#1} = \dsub{Sum of selected}{Sum of ranks}
	\]
}
\newcommand{\singsel}[1]
{
	\[
		\tsub{Score}{#1} = \dsub{Rank of selected}{Max. rank}.
	\]
}
\newenvironment{ttable}
{
\begin{center}
\begin{tabular}{c|c}
\hline
}
{
\\ \hline
\end{tabular}
\end{center}
}

\begin{document}
\maketitle

%% BODY %%
\section{About the document}
This file documents the process of asset tagging for the asset 'Information Center' in the vertical 'Panchayati Raj'.

\section{Attributes and questions}
The list of sections, variables, and questions are:
\begin{itemize}
	\item Observation
	\item General
	\item Asset Specific
		\begin{itemize}
			\item Availability
				\begin{enumerate}
					\item Services:  Which of the following services are available in the center?
				\end{enumerate}
			\item Service
				\begin{enumerate}
					\item Reach: How many people visit the information center in a week?
				\end{enumerate}
			\item Facility
				\begin{enumerate}
					\item Services: What other facilities does the information center offer?
				\end{enumerate}
		\end{itemize}
\end{itemize}

\section{Overall scoring}
The overall scoring of the asset is given as,
\begin{align*}
	\tsub{Score}{asset} &= \tsubb{W}{observation} \times \tsub{Score}{observation} \\
	&+ \tsubb{W}{general} \times \tsub{Score}{general} \\
	&+ \tsubb{W}{specific} \times \tsub{Score}{specific}.
\end{align*}

The score of a section or a variable is given as,
\[
	\tsub{Score}{var} = \sum_{l \in P} \tsubb{W}{l} \times \tsub{Score}{l}.
\]
where,
\[
	P = \text{Set of sub-parameter labels.}
\]	

\section{Attribute scoring and the process}
\subsection{Asset Specific}
\subsubsection{Availability}
\paragraph{Services: Which of the following services are available in the center?}
The options given are,
\begin{ttable}
	Services & Rank \\ \hline
	Others & 1 \\
	Payment of bill & 2 \\
	Banking & 3 \\
	Issue of Official documents & 3 \\ \hline
	Sum of ranks & 9
\end{ttable}
The score is given as,
\multsel{availability}
\subsubsection{Service}
\paragraph{Reach: How many people visit the information center in a week?} 
The score is given as,
\begin{align*}
	\tsub{Score}{service} &= 1, \tsubb{N}{visitors} \ge \text{Threshold} \\
	&= \Big( \dfrac{\tsubb{N}{visitors}}{\text{Threshold}} \Big)^{2}, \text{Otherwise}.
\end{align*}

\subsubsection{Facility}
\paragraph{Services: What other facilities does the information center offer?}
The options given are,
\begin{ttable}
	Services & Rank \\ \hline
	Printing & 1 \\
	Scanning & 1 \\
	Photocopy & 1 \\
	Lamination & 1 \\ \hline
	Sum. of ranks & 4
\end{ttable}
The score is given as,
\multsel{facility}
\paragraph{Suggestion} The variable facility is treated as a multi-choice multi-select option.
\end{document}

