\documentclass[oneside]{article}

\title{Conventions and Considerations}
\author{Kipa Tachak}
\date{Thursday 30 May 2019}

\setcounter{secnumdepth}{0}

\begin{document}
\maketitle

\section{Instruction on work}
\begin{enumerate}
\item create individual directories for each problem areas.
E.g. education, agriculture etc.
\item In the directories for each problem area put the
files related to assed tagging and name the files according
to the asset being tagged. E.g. \texttt{it\_vocational\_training\_center},
\texttt{degree\_college\_upto\_ug}, etc.
\item Follow the instructions below.
\end{enumerate}

\section{Document structure}
The documents should be structured as follows:
\begin{enumerate}
\item About the document: brief description of the content.
\item Attributes for scoring the asset: A complete list of
variables and their sub-paramters.
\item Overall score: scoring for asset.
\item Attribute scoring and the process: Scoring of attributes
and the thorough explaination of the process.
\item Comments and Suggestion: An overall and general comments
and suggestions regarding the questionare and analysis. However,
specific suggestions can be added to section of interest.
\end{enumerate}

\section{Scoring plan}
The scoring of the variables will be done as follows:
\begin{enumerate}
\item Scoring of sub-variables: The sub-variables will be score
on a scale of 0 to 1. The scoring will be based on the input of
the questions and the type of the questionare.
\item Scoring of the main-variables:
The main-variables will be scored on a scale of 0 to 100.
The scoring will be done combining the scores of each
sub-variable multiplied by some weight.
\end{enumerate}

\section{Constraints on weights}
We have not allocated the weights. That is for the expert
in social sciences to do. However, the equations are chosen
assuming the sub-variables contribute some fraction to the
total score. This fraction is decided by the weights assigned.

But, the following constraints are to be kept in mind when
assigning the weights.
\begin{enumerate}
\item The weights should be assigned in such a way that when
the individual sub-parameters are in their maximum assignable
score, the score of the variable should be its maximum
assignable score.
\item If the individual sub-parameters are in their minimum
assignable score, the score of the the score of the variable
should be its minimum assignable score.
\end{enumerate}
\end{document}
